```{r global_options, include=FALSE}
knitr::opts_chunk$set(warning=FALSE, message=FALSE)
```
---
title: "Project Report
author: "Hetian Chen"
date: "Sep 11, 2015"
---

## Introduction  
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement – a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior, or because they are tech geeks. One thing that people regularly do is quantify how much of a particular activity they do, but they rarely quantify how well they do it.  

In this project, we will use data from accelerometers on the belt, forearm, arm, and dumbell of 6 participants to predict the manner in which they did the exercise.  

## Load Packages
```{r, cache = T}
library(caret)
library(rpart)
library(rpart.plot)
library(randomForest)
library(corrplot)
```
## Data Preprocessing

In this step, we deleted the observations with missing data and delete the attributes that are not likely to 
contribute to the prediction. At last, we got a clean training set with 19622 observations and 53 variables

```{r, cache = T}
trainRaw <- read.csv("data/pml-training.csv")
testRaw <- read.csv("data/pml-testing.csv")
sum(complete.cases(trainRaw))
trainRaw <- trainRaw[, colSums(is.na(trainRaw)) == 0] 
testRaw <- testRaw[, colSums(is.na(testRaw)) == 0]
classe <- trainRaw$classe
trainRemove <- grepl("^X|timestamp|window", names(trainRaw))
trainRaw <- trainRaw[, !trainRemove]
trainCleaned <- trainRaw[, sapply(trainRaw, is.numeric)]
trainCleaned$classe <- classe
testRemove <- grepl("^X|timestamp|window", names(testRaw))
testRaw <- testRaw[, !testRemove]
testCleaned <- testRaw[, sapply(testRaw, is.numeric)]
dim(trainCleaned)
dim(testCleaned)
```

## Data Modeling and Evaluation on 3-fold Cross Validation 

**Random Forest** algorithm was chosen in this task becuase it's robust to correlated covariates and outliers.
A **3-fold cross validation** was applied on the "train" set to evaluate the performance of the algorithm. According to the results, the estimated out-of sample error is about

```{r, cache = T}
controlRf <- trainControl(method="cv", 3)
modelRf <- train(classe ~ ., data=trainCleaned, method="rf", trControl=controlRf, ntree=250)
modelRf
```

## Make Prediction of the Test Data Set

```{r, cache = T}
result <- predict(modelRf, testCleaned[, -length(names(testCleaned))])
result
```  







